# Frequently Asked Questions:

### What is the purpose of this package?
The purpose of this package is to perform genome-wide associations. It implements covariates supplied by the user, as well as other covariates in the form of principle components generated from the genotype data as fixed effects in a general linear model.  

### What format should my genotype data be in for use in this package?
Genotypic data should be in numeric matrix/dataframe format with taxa as rows and markers as columns. The first column need not contain the taxa ID, as long as the order is known to the user (i.e. they are non-essential for the function to run).  
  
  
    
An example:  
```{r genotype example, echo=F}
gen.data <- read.table(file="http://zzlab.net/GAPIT/data/mdp_numeric.txt",head=T)
gen.data[1:5, 1:5]
```
Source: [http://zzlab.net/GAPIT/data/mdp_numeric.txt](http://zzlab.net/GAPIT/data/mdp_numeric.txt)  
  
  
  
### What format should my phenotype data be in for use in this package?
Phenotypic data should be in a numeric matrix/dataframe formate with taxa as rows and a phenotype measure column. Only one phenotype should be present. Again, the first column does not need to contain the taxa ID (i.e. it can be a one column matrix)  
  
  
An example:
```{r phenotype example, echo=F}
phen.data <- read.table(file="http://zzlab.net/GAPIT/data/CROP545_Phenotype.txt",head=T)
phen.data[1:5, 1:2]
```
Source: [http://zzlab.net/GAPIT/data/CROP545_Phenotype.txt](http://zzlab.net/GAPIT/data/CROP545_Phenotype.txt)  
  
  
  
### What format should my covariate data be in for use in this package?
Covariate data should be formatted in the same way as phenotypic data--taxa as rows and covariates in subsequent columns.  
  
An example:
```{r covariate example, echo=F}
covs <- read.table(file="http://zzlab.net/GAPIT/data/CROP545_Covariates.txt",head=T)
covs[1:5, 1:3]
```
Source: [http://zzlab.net/GAPIT/data/CROP545_Covariates.txt](http://zzlab.net/GAPIT/data/CROP545_Covariates.txt)  
  
  
  
### How are Principle Components generated?  
Principle components are generated through use of the 'stats' package's function prcomp()  
  
  
### Is there any risk of redundancy between my covariates and the principle components calculated?  
No, the filter.pca() function in this package takes care of that. This function is called inside of the GLM.func() function, which acts as the major workhorse function of the package.  
  
  
### Wow, you guys seem very smart, did you come up with all these functions independently?  
NO! These functions borrow heavily, or are identical to scripts from our CROPS_545 course at WSU taught by the fabled Dr. Zhiwu Zheng and TA'd by the more-than-capable Matthew McGowan. But we're flattered you thought that.
